A Connection Between Star Formation Rate and Dark Matter Halos at $Z\sim6$ In 2013 Planck Cosmology.

### 2014-06-20 paper/fitting_model.tex
SFR, Fitting Model, The_Bibliography

\section{The Fitting Model}

  This fitting model contains four parameters: $\left(m/M\right)_0$, $M_1$, 
$\beta$ and $\gamma$, 
  where $m:=$ Stellar mass, and $M :=$ Dark Matter Halo mass.
  \begin{equation}
  \frac{m}{M} = 2 \left( \frac{m}{M} \right)_{0} 
		    \left[ \left(\frac{M}{M_1}\right)^{-\beta} + 
\left(\frac{M}{M_1}\right)^{\gamma} \right]^{-1} 
  \end{equation}
  This is similar to the proposed by \cite{moster10}.
  Another model cited in the article contains five parameters: $m_0$, $M_1$, 
$\beta$, $\gamma_1$ and $\gamma_2$.
  \[ m(M) = m_0 \frac{ (M/M_1)^{\gamma_1}}{ \left[ 1 + (M/M_1)^\beta \right]^{ 
(\gamma_1-\gamma_2)/\beta}} \]

   ``We use a statistical approach to determine the relationship between the 
stellar masses of galaxies and the masses
  of the dark matter halos in which they reside. We obtain a parameterized 
stellar-to-halo mass (SHM) relation by
  populating halos and subhalos in an N-body simulation with galaxies and 
requiring that the observed stellar mass
  function be reproduced.'' \citep{moster10}

>>>>

\section{The Fitting Model}
The model links dark matter and U-luminosity by a four parameter function.
For each galaxy we have the luminosity:
  \begin{equation}
  L = L_{0} M \left[ \left( \frac{M}{M_0}\right)^{-\beta} 
		   + \left( \frac{M}{M_0}\right)^{\gamma} 
               \right]^{-1}
  \end{equation}
where $M$ is the hosting DMH mass, $L_{0}$ is a normalization constant, $M_0$
is the critical mass where the luminosity function has a slope change, 
$\beta$ and $\gamma$ are the slopes.
This relation can reproduce the luminosity function with best agreement than the classical Schechter function wich works good for low redshift galaxies.

This equation has a similar fashion to the mass to light relation \citep{vandenbosch03} and the mean relation between stellar mas of a galaxy and the mas of its halo used by \cite{moster10}.

### 2014-06-20 paper/introduction.tex
SFR, Fitting Model, The_Bibliography

  The HMF is created using the DMH catalog from the Multidark Database 
\citep{riebe13}.

@@

  Is important to know and understand the existence of local fluctuations   or 
inhomogeneities due the observed scale.  For this part is necesary to study the 
HMF on smaller boxes

\section{Relationship between Galaxy Luminosity Function (GLF) and
  Dark Matter Halo (DMH) mass}

  In one hand we have observational results: the GLF for star-forming galaxies 
at high redshift (z=5.9)\citep{bouwens06,willott13}  expressed in terms of 
magnitude in the ultraviolet range (M1350). In the other hand we have a DMH  
catalog, result from the Multidark Simulation with Plank Cosmology. 
%\citep{Multidark}

  A $1000 \textrm{ Mpc} ^3 \textrm{h}^{−3}$ cubic box containing near to  
$11\times10^6$ dark matter halos.

  The idea is to connect the observed GLF with the DMH catalog. We assume that  
each halo contains one and just one galaxy, and its luminosity is given by:
  \begin{equation}
  L_\textrm{galaxy}=\alpha M_\textrm{halo}^\beta 
  \end{equation}
but this function is given in magnitude units. Is necesary to convert 
magnitude to luminosity.

  \subsection{Magnitude to Luminosity}
  The Luminosity is an intrinsic propertie of the stars. It doesn't deppends of 
the distance.  It's directly related to the energy flux emmited. The luminosity 
$L_\nu$ at a given frecuency $\nu$ has $[\textrm{W}\textrm{Hz}^{-1}]$ or 
$[\textrm{erg}\textrm{s}^{-1}\textrm{Hz}^{-1}]$ units.

  The magnitude is brightnes star classification inherited from ancient Greeks. 
It deppends of the stellar distance. The absolute magnitude is a modern 
classification independent of  distance. Taking the Sun as reference, the 
absolute magnitud at a given wavelengt is given by: 
 \[ M_{\lambda} = M_{\lambda \odot} - 2.5 \log_{10}\left( 
\frac{L_\lambda}{L_{\lambda \odot}} \right) \]
  The solar absolute magnitude in the U filter is $M_{U\odot} = 5.61$,
and the solar luminosity in the same filter is $L_{U\odot} = 10^{18.48} 
\textrm{ergs s}^{-1}\textrm{Hz}^{-1}$ or $ L_{U\odot} = 3.02 \times 10^{18} 
\textrm{ergs s}^{-1}\textrm{Hz}^{-1}$.

  Replacing in the absolute magnitude equation:
  \[ M_{U} = 5.61 - 2.5 \log_{10}(L_{U}) + 2.5\times18.48\]
  gives the magnitude in the U filter of an astrophysical source:
  \[ M_{U} = 51.82 - 2.5 \log_{10}(L_{U}) \]

  \subsection{Best Fitting Parameters}

>>>>

%  The HMF is created using the DMH catalog from the Multidark Database 
%\citep{riebe13}.

@@

%  Is important to know and understand the existence of local fluctuations   or 
%inhomogeneities due the observed scale.  For this part is necesary to study the 
%HMF on smaller boxes

\section{Linking Galaxy Luminosity Function (GLF) and
  Dark Matter Halo (DMH) mass}

%  In one hand we have observational results: the GLF for star-forming galaxies 
%at high redshift (z=5.9)\citep{bouwens06,willott13}  expressed in terms of 
%magnitude in the ultraviolet range (M1350). In the other hand we have a DMH  
%atalog, result from the Multidark Simulation with Plank Cosmology. 
%\citep{Multidark}

 % A $1000 \textrm{ Mpc} ^3 \textrm{h}^{−3}$ cubic box containing near to  
%$11\times10^6$ dark matter halos.

%  The idea is to connect the observed GLF with the DMH catalog. We assume that  
%each halo contains one and just one galaxy, and its luminosity is given by:
%  \begin{equation}
%  L_\textrm{galaxy}=\alpha M_\textrm{halo}^\beta 
%  \end{equation}
%but this function is given in magnitude units. Is necesary to convert 
%magnitude to luminosity.

\subsection{Magnitude to Luminosity}

Luminosity Functions (LF) are usually expressed in terms of magnitude instead 
luminosity. Luminosity is the energy emmited by a source in a given wavelengt range, 
is a physical quantity. 
%The luminosity 
%$L_\nu$ at a given frecuency $\nu$ has $[\textrm{W}\textrm{Hz}^{-1}]$ or 
%$[\textrm{erg}\textrm{s}^{-1}\textrm{Hz}^{-1}]$ units.
Magnitude is a classification inherited from ancient Greeks, this
quantifies the response of the first astrometric device: the human eye, this
perception grows loarithmically with the retrieved radiation.

Taking the Sun as reference, the absolute magnitud at a given wavelengt is given by: 
 \[ M_{\lambda} = M_{\lambda \odot} - 2.5 \log_{10}\left( 
\frac{L_\lambda}{L_{\lambda \odot}} \right) \]
  The solar absolute magnitude in the U filter is $M_{U\odot} = 5.61$,
and the solar luminosity in the same filter is $L_{U\odot} = 10^{18.48} 
\textrm{ergs s}^{-1}\textrm{Hz}^{-1}$ or $ L_{U\odot} = 3.02 \times 10^{18} 
\textrm{ergs s}^{-1}\textrm{Hz}^{-1}$. The solar luminosity can be used as
refference unit, in this fashion, the typical luminosity of a galaxy can be expresed in
terms of $10^{8}-10^{11}$ times the sun luminosity.

  The absolute magnitude of a galaxy equation in the U filter:
  %\[ M_{U} = 5.61 - 2.5 \log_{10}(L_{U}) + 2.5\times18.48\]
  %gives the magnitude in the U filter of an astrophysical source:
  \[ M_{U} = 51.82 - 2.5 \log_{10}(L_{U}) \]

 %\subsection{Best Fitting Parameters}
